Placeholder

### 2021-02-16 Paper_Histograms.Rmd
Get sign up numbers per month by participant sample

>>>>

##Sign-up histogram

```{r Get GLAD/EDGI participant sign-up data}

#Visualise some dates when participants completed the questionnaire
head(dat.retro$startDate.coping, 10)

#Divide the data by sign up per month and summarise the amount of pt's completing the survey that month

dat.retro_april_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-04-"), ] %>% 
  select(Sample_plot, startDate.coping) %>%
  group_by(Sample_plot) %>% 
  summarise(April = n())

dat.retro_may_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-05-"), ] %>% 
  select(Sample_plot, startDate.coping) %>% 
  group_by(Sample_plot) %>% 
  summarise(May = n())

dat.retro_june_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-06-"), ] %>% 
  select(Sample_plot, startDate.coping) %>% 
  group_by(Sample_plot) %>% 
  summarise(June = n())

dat.retro_july_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-07-"), ] %>% 
  select(Sample_plot, startDate.coping) %>% 
  group_by(Sample_plot) %>% 
  summarise(July = n())

dat.retro_august_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-08-"), ] %>%
  select(Sample_plot, startDate.coping) %>% 
  group_by(Sample_plot) %>% 
  summarise(August = n())

dat.retro_september_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-09-"), ] %>% 
  select(Sample_plot, startDate.coping) %>% 
  group_by(Sample_plot) %>% 
  summarise(September = n())

#Merge results into one tibble

dat.retro_sign_up <- dat.retro_april_sign_up %>% 
  cbind(dat.retro_may_sign_up,
        dat.retro_june_sign_up,
        dat.retro_july_sign_up,
        dat.retro_august_sign_up,
        dat.retro_september_sign_up)

#Gather the variables
dat.retro_sign_up <- dat.retro_sign_up %>% 
  gather(key = "month", value = "n")

head(GLAD.retro_sign_up, 10)
